---
title: "Uher Assignment 2"
author: "Michael Uher"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

#SETUP

Importing provided data "UniversalBank.xlsx".

```{r}
library(caret)
library(class)
library(readxl)

UniversalBank <- read_excel("C:/Users/Mike/Downloads/UniversalBank.xlsx")
```

Splitting the dataset into 60% training data and 40% testing data.

```{r}
set.seed(123)

Train_Index <- createDataPartition(UniversalBank$`Personal Loan`, p = 0.60, list = FALSE)

Train <- UniversalBank[Train_Index, ]
Test <- UniversalBank[-Train_Index, ]
```

Removing the ID and ZIP Code columns from the training and testing data, as well as splitting up the Education variable into 3 variables for easier identification and removing the old variable.

```{r}
Train <- Train[, !(names(Train) %in% c("ID", "ZIP Code"))]
Test <- Test[, !(names(Test) %in% c("ID", "ZIP Code"))]

Train$Education_1 <- ifelse(Train$Education == 1, 1, 0)
Train$Education_2 <- ifelse(Train$Education == 2, 1, 0)
Train$Education_3 <- ifelse(Train$Education == 3, 1, 0)

Test$Education_1 <- ifelse(Test$Education == 1, 1, 0)
Test$Education_2 <- ifelse(Test$Education == 2, 1, 0)
Test$Education_3 <- ifelse(Test$Education == 3, 1, 0)

Train$Education <- NULL
Test$Education <- NULL
```

Creation of predictor variables without the "Personal Loan" variable, and response variables.

```{r}
Train_Predictors <- Train[, names(Train) != "Personal Loan"]
Test_Predictors <- Test[, names(Test) != "Personal Loan"]

Train_Y <- factor(Train$`Personal Loan`)
Test_Y <- factor(Test$`Personal Loan`)
```

Standardizing the variables to give them equal weight and create the response variable.

```{r}
preprocess <- preProcess(Train_Predictors, method = c("center", "scale"))

Train_Normalized <- predict(preprocess, Train_Predictors)
Test_Normalized <- predict(preprocess, Test_Predictors)
```

Creating the final training data.

```{r}
Train_Final <- data.frame( Train_Normalized, 'Personal Loan' = Train_Y)
```

#Question 1

Create the customer listed in question 1 and order the columns properly.

```{r}
Customer1 <- data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Mortgage = 0, 'Securities Account' = 0, 'CD Account' = 0, Online = 1, CreditCard = 1, Education_1 = 0,  Education_2 = 1, Education_3 = 0, check.names = FALSE)

Customer1 <- Customer1[, names(Train_Predictors)]
```

Normalizing the customer data and doing a kNN analysis where k = 1.

```{r}
Customer1_Normalized <- predict(preprocess, Customer1)

Customer1_KNN <- knn(Train_Normalized, Customer1_Normalized, Train_Y, k = 1)

Customer1_KNN
```
The Customer with the data given above would be classified as not being accepted for the loan.

#Question 2

Testing k of different values with the same seed to find the best possible k value.
```{r}
set.seed(123)

suppressWarnings(Test_KNN <-train(Train_Normalized,Train_Y, method="knn", tuneGrid=expand.grid(k=c(1:20))))

suppressWarnings(Test_KNN)
```
Out of the range 1:20, it is found that k = 1 is the best value of k with the highest accuracy.

#Question 3

Creating a confusion matrix showing the performance of the best value of k using the validation data.
```{r}
Test_Predictions <- knn(train = Train_Normalized, test = Test_Normalized, cl = Train_Y, k = 1)

Confusion_Matrix <- confusionMatrix(Test_Predictions, Test_Y, positive = "1")
Confusion_Matrix

table(Predicted = Test_Predictions, Actual = Test_Y)
```
Overall accuracy is about 96.4%, better than the baseline accuracy of 90.4% from the problem.

#Question 4

Predicting the customer listed with a value of k = 1.
```{r}
Customer1_BestK <- knn(train = Train_Normalized, test = Customer1_Normalized, cl = Train_Y, k = 1)
Customer1_BestK

```
The customer listed would not be accepted for a loan.